Stable individual differences in strategies within, but not between, visual search tasks

### 2019-02-22 Manuscript/manuscript.tex
Chopped more words  from discussion. Should now be fine!

\begin{figure*}
\centering
\subfigure[][]{\includegraphics[height=3cm]{figures/split-half.png}}
\subfigure[][]{\includegraphics[height=3cm]{figures/adaptive.png}}
\subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
\caption{Example stimulus from the (a) \textit{split-half line segment} (SHLS), (b) \textit{adaptive choice visual search} (ACVS) and (c) \textit{mouse click foraging task} (MCFT) paradigms.}
\label{fig:exampleStimuli}
\end{figure*}

@@

We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments. Surprisingly, however, the between-paradigm correlations give $R^2 \approx 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from  0.58 to 0.92.

There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise. The test-retest correlations on each of the individual visual search tasks rule out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation. One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's speed-accuracy trade-off, motivation or conscientiousness might lead to better or worse overall performance across all the tasks. However, what we did observe were high correlations between our measures of strategy and reaction time within each task, suggesting our strategy metrics determine a large proportion of search performance, and reinforcing the interpretation that an individual who is strategic in one task is not necessarily strategic in the others.

Although the tasks in this experiment all have visual search in common, they also have unique aspects that appear to have resonated with particular individuals' strengths, and not others. Our definition of a successful strategy in the SHLS task was fixating the locations that provide new information. In the ACVS task, a successful strategy meant appropriately altering search goals to match changes in the environment. In the MCFT task, success involved minimizing cognitive load by minimizing target switching. Each of these tasks clearly taps into unique aspects of visual search strategies, and performance on one has little bearing on the others.

Individual differences pose a challenge for efforts to devise a comprehensive model of visual search. Our understanding of the mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure their effects on averaged performance. This approach has led to important insights, for example, about the kinds of visual features that can guide attention (e.g.  \citep{treisman1980, wolfe2007}; how attentional control settings filter  distractors (e.g.  \citep{folk1992,yantis1999}); and biases in attention, such as a bias towards unexplored locations (e.g.  \citep{klein2000}). For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals' performance. In the original SHLS study  \citep{nowakowska2017}, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \citep{najemnik-geisler2008}, versus a stochastic  \citep{clarke2016}, model. Considering only the average search performance, the stochastic model was a good explanation. Underlying that average performance, however, was a large spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither. The original question needed to be refined into new question: for whom is search optimal and for whom is it stochastic? The current findings add even further challenges for researchers interested in understanding visual search, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.

We view these findings not as a discouraging result, but as thought-provoking and exciting. Vogel and Awh \citep{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms. Our results suggest that context and structure of the task also needs to be taken into account. Understanding how an individual's behaviour varies across different search tasks can lead to the development of a more comprehensive theory of search.

>>>>

\begin{figure}
\centering
\subfigure[][]{\includegraphics[height=3cm]{figures/split-half.png}}
\subfigure[][]{\includegraphics[height=3cm]{figures/adaptive.png}}
\subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
\caption{Example stimulus from the (a) \textit{split-half line segment} (SHLS), (b) \textit{adaptive choice visual search} (ACVS) and (c) \textit{mouse click foraging task} (MCFT) paradigms.}
\label{fig:exampleStimuli}
\end{figure}

@@

We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments. Surprisingly, however, the between-paradigm correlations give $R^2 \approx 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually.

There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise. The test-retest correlations on each of the individual visual search tasks rule out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation. One might have expected reaction time to be at least modestly correlated from one search task to the next, as a general factor like an individual's speed-accuracy trade-off, or motivation might lead to better or worse overall performance. However, we did observe correlations between measures of strategy and reaction time within each task, suggesting our strategy metrics determine a large proportion of search performance.

Although the tasks in this experiment all have visual search in common, they also have unique aspects that appear to have resonated with particular individuals' strengths, and not others. Our definition of a successful strategy in the SHLS task was fixating the locations that provide new information. In the ACVS task, a successful strategy meant appropriately altering search goals to match changes in the environment. In the MCFT task, success involved minimizing cognitive load by minimizing target switching. Each of these tasks taps into unique aspects of visual search strategies, and performance on one has little bearing on the others.

Individual differences pose a challenge for efforts to devise a comprehensive model of visual search. Our understanding of the mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure effects on averaged performance. This approach has led to important insights, for example, about the kinds of visual features that can guide attention (e.g.  \citep{treisman1980, wolfe2007}; how attentional control settings filter  distractors (e.g.  \citep{folk1992,yantis1999}); and biases in attention, such as a bias towards unexplored locations (e.g.  \citep{klein2000}). For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals' performance. In the original SHLS study, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \citep{najemnik-geisler2008}, versus a stochastic  \citep{clarke2016}, model. Considering only the average performance, the stochastic model was a good explanation. Underlying that average performance, however, was a spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither. The original question needed to be refined: for whom is search optimal and for whom is it stochastic? The current findings add even further challenges for researchers, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.

We view these findings not as a discouraging result, but as thought-provoking and exciting. Vogel and Awh \citep{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms. Our results suggest that context and structure of the task also needs to be taken into account. Understanding how an individual's behaviour varies across different search tasks can lead to the development of a comprehensive theory of search.
